Phenotype selection

### 2021-11-25 analysis/phenotype_selection.Rmd
use `traits_corr2_filled` in couple correlation Rmd so all traits have a category.

tar_load(data_phesant_directory)
tar_load(Neale_SGG_dir_filt)
tar_load(traits_corr)
tar_load(traits_corr2)
tar_load(traits_corr3)
tar_load(traits_corr4)
tar_load(traits_corr5)
tar_load(traits_corr6)

@@

traits_corr2.DT <- traits_corr2 %>% as_tibble() %>% mutate(r = sqrt(r2)) %>% dplyr::select(Neale_pheno_ID, description, variable_type, category, N_pairs, r2, r) %>% unique()
DT::datatable(traits_corr2.DT, width = "100%") %>% formatRound(columns=c('r2', 'r'), digits = 3)
```

>>>>

tar_load(data_phesant_directory)
tar_load(Neale_SGG_dir_filt)
tar_load(traits_corr)
tar_load(traits_corr2)
tar_load(traits_corr2_filled)
tar_load(traits_corr3)
tar_load(traits_corr4)
tar_load(traits_corr5)
tar_load(traits_corr6)

@@

traits_corr2.DT <- traits_corr2_filled %>% as_tibble() %>% mutate(r = sqrt(r2)) %>% dplyr::select(Neale_pheno_ID, description, variable_type, category, N_pairs, r2, r) %>% unique()
DT::datatable(traits_corr2.DT, width = "100%") %>% formatRound(columns=c('r2', 'r'), digits = 3)
```
